### 2013-09-18 chi2014/abstract.tex
abstract, introduction pass

In this paper we describe the formatting requirements for
SIGCHI Conference Proceedings, and this sample file
offers recommendations on writing for the worldwide
SIGCHI readership. Please review this document even if
you have submitted to SIGCHI conferences before, some
format details have changed relative to previous years.

>>>>

Microtask marketplaces enable hybrid computational systems that use crowds to solve problems of creativity, such as brainstorming. We present a first characterization of brainstorming in this context, providing models for the rate of idea generation, the rate of category generation, the originality of ideas and the novelty of ideas. We demonstrate that the rates of idea and category generation can be closely fit by a logarithmic model, that these rates roughly increase if fewer participants are asked for more responses, and that this distinction is the result of a \emph{burn in period} of common ideas at the beginning of a brainstorming task. Furthermore, we explore the phenomenon of \emph{riffing} in brainstorming tasks, and replicate two related findings from prior work. Our results provide recommendations for those leveraging the crowd for brainstorming, and comparable models of creative idea generation research community.

### 2013-09-18 chi2014/introduction.tex
abstract, introduction pass

Microtask marketplaces such as Amazon's Mechanical Turk have proven to be useful platforms for outsourcing a wide range of tasks, from proofreading documents \cite{soylent} to estimating the caloric content of pictures of food \cite{platemate}.  These platforms make possible human computation systems \cite{quinn_2011}, hybrid computational systems that tap humans' abilities to solve problems that currently cannot be solved by machines alone.

@@

In this paper, we focus on crowd-based brainstorming. While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that specifically describes and models the brainstorming process in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006} OTHERS?), microtask marketplaces are qualitatively different from previously studied environments, calling into question how much of this past research maps onto this environment. For example, brainstorming participants in a microtask marketplace are paid for their participation, and are often eager to complete a task as fast as possible to move on to the next paying task [REF?]. Given these and other differences, there are many open questions about how brainstorming unfolds in this context.

@@

This paper presents results from a series of experiments intended to model brainstorming on microtask marketplaces (specifically, Amazon's Mechanical Turk). In our experiments, we asked individuals to brainstorm ways to use an MP3 player whose batteries were dead. We varied the number of ideas requested (5, 10, 20, 50, 75, 100, or unlimited), paying a fixed amount per idea (3.5 cents). Across all conditions, 154 workers submitted responses to 170 HITs (Human Intelligence Tasks), yielding 3292 ideas. From these ideas, we present a series of models characterizing features of crowd brainstorming, such as the rate of novel idea production, the rate at which novel {\em categories\/} of ideas are produced (where a category represents a set of conceptually similar ideas that are distinct from other categories), and the relative novelty of ideas, all as functions of number of responses requested.

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow logarithmic growth models, as a function of the total number of responses received, from all participants. In other words (and as one would expect), there are diminishing returns from asking more people to submit ideas. However, the actual rates differ per condition, as described below
\item The rates for generating novel ideas are linked to the number of responses requested: The more responses requested from individuals, the higher the rate of novel idea generation, in general. [TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Our data suggest that the first 20 ideas are the most unoriginal (i.e., the most common). This finding complements the previous finding, and further suggests that there is little value in requesting fewer than 20 ideas from workers
\item Individuals' patterns of idea generation mimic those identified by Nijstaf and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. In our data, we see the prevalence of riffing steadily increase over the first 20 responses, after which its prevalence plateaus
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 20)
\item The time spent producing an idea matches the times reported in previous studies \cite{nijstad_how_2006}
\end{itemize}

>>>>

Microtask marketplaces such as Amazon's Mechanical Turk have proven to be useful platforms for outsourcing a wide range of tasks, from proofreading documents \cite{soylent} to estimating the caloric content of food \cite{platemate}.  These platforms make possible human computation systems \cite{quinn_2011}, hybrid systems that tap humans' abilities to solve problems that currently cannot be solved by machines alone.

@@

In this paper, we focus on crowd-based brainstorming. While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that specifically describes and models the brainstorming process in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006} OTHERS?), microtask marketplaces have qualitative differences. For example, brainstorming participants in a microtask marketplace are paid for their participation, and are often eager to complete a task as fast as possible to maximize earnings [REF?]. Furthermore, participants in microtask marketplaces cannot be expected to be spatially or temporally co-located. There many open questions about how brainstorming unfolds in this context.

@@

This paper presents the results of a series of experiments intended to model brainstorming on microtask marketplaces (specifically, Amazon's Mechanical Turk). In our experiments, we asked individuals to brainstorm ways to use an MP3 player whose batteries were dead. We varied the number of ideas requested (5, 10, 20, 50, 75, 100, or unlimited), paying a fixed amount per idea (3.5 cents). Across all conditions, 154 workers submitted responses to 170 HITs (Human Intelligence Tasks), yielding 3292 ideas. From these ideas, we present a series of models characterizing features of crowd brainstorming, such as the rate of novel idea production, the rate at which novel {\em categories\/} of ideas are produced (where a category represents a set of conceptually similar ideas that are distinct from other categories), and the relative novelty of ideas, all as functions of number of responses requested.

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow logarithmic growth models, as a function of the total number of responses receieved across participants. Thus, the rate of novel ideas decreases exponentially. 
\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. [TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. The first 20 ideas are the least original (i.e., the most common). This finding complements the previous finding, and further suggests that there is little value in requesting fewer than 20 ideas from workers
\item Individuals' patterns of idea generation mimic those identified by Nijstaf and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. In our data, we see the prevalence of riffing steadily increase over the first 20 responses, after which its prevalence plateaus
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 15)
\item The time spent producing an idea matches the times reported in previous studies \cite{nijstad_how_2006}
\end{itemize}
